\documentclass[lualatex,aspectratio=169]{beamer}

\usepackage{ulem}
\usepackage{fontspec}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{bbold}
\usepackage{qrcode}
\usepackage{caption}
\usepackage{ccicons}

\beamertemplatenavigationsymbolsempty

\setmonofont{Inconsolata}
\newfontfamily\emojifont[Renderer=HarfBuzz]{NotoColorEmoji}
\newfontfamily\cjkfont{Noto Sans CJK JP}
\newfontfamily\symbolfont{DejaVu Sans}

\title{I Quit}
%\subtitle{(my job)}
\author{Penbu}
\date{February 4, 2025}

\begin{document}
  \frame{\titlepage\begin{center}\small{}This work is licensed under the \href{http://creativecommons.org/licenses/by/4.0/}{CC BY 4.0} \ccby\end{center}}

  \begin{frame}
    \frametitle{What happened?}
    \pause
    I quit \pause my job.

    \pause
    And I'm taking a career break for a year.
  \end{frame}

  \begin{frame}
    \frametitle{When?}
    \pause
    Last Friday.

    \pause
    But actually mid-November.
  \end{frame}

  \begin{frame}
    \frametitle{Why?}
    \pause

    I don't know what I want to do anymore.
  \end{frame}

  \begin{frame}
    \frametitle{What does this mean?}
    \pause I'm now officially a NEET\@.

    \pause The meme of the full-time vtuber is real.

    \pause
    \vfill

    \begin{block}{Definition}
      \begin{description}
        \item[NEET] ``Not in Education, Employment, or Training''
      \end{description}
    \end{block}
  \end{frame}

  \begin{frame}
    \frametitle{Should you do this?}
    \pause
    Probably not.
    \pause
    But maybe.
  \end{frame}

  \begin{frame}
    \frametitle{What does this mean going forward?}
    \pause
    \begin{itemize}[<+->]
      \item More consistent streams
      \item More streams that require prep
      \item More video uploads
      \item Progress on stalled projects
      \item Collabs with people in other timezones
    \end{itemize}
  \end{frame}

  \begin{frame}
    \frametitle{What goals do I have for the immediate future?}
    \pause
    \begin{itemize}[<+->]
      \item Polish and release ``Looking Back''
      \item Polish and release ``Pieces''
      \item Work on the mix for ``All You've Done''
      \item Finish converting the website to Svelte
      \item More monetization options
      \item More Tetris content on a second channel
    \end{itemize}
  \end{frame}

  \begin{frame}
    \centering
    \begin{beamercolorbox}[sep=12pt,center]{section title}
      \usebeamerfont{section title}What questions do you have?
    \end{beamercolorbox}
  \end{frame}

\end{document}
